Staged Abstract Interpreters

### 2018-10-18 paper/abstract.tex
continue working on outline

In this paper, we study \textit{abstract} interpreters with multi-stage programming, i.e., the 
staged abstract interpreters. 
By staging an abstract interpreter respect to a program, we obtain a compiled and faster analysis.
By appying the idea to \textit{open} programs, we obtain a modular analysis that generates sound
partial analysis results which can be composed and reused later without losing precision, though 
the original abstract interpreter is a whole-program analysis algorithm.

>>>>

In this paper, we study \textit{abstract} interpreters with multi-stage programming, i.e., the 
staged abstract interpreters. 
By staging an abstract interpreter respect to a program, we obtain a specialized analysis that runs faster.
By appying the idea to \textit{open} programs and considering the free variables as dynamic inputs, 
we obtain a modular analysis that generates sound partial analysis results which can be composed 
and reused later without losing precision, though the original abstract interpreter is a whole-program 
analysis algorithm.
